Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-11-15 manuscript/manuscript.tex
typo

In addition to publications on the theory and application of Markov state modeling~\cite{schuette-msm,buchete-msm-2008,noe-tmat-sampling,bowman-msm-2009,noe-folding-pathways,sarich-msm-quality,noe-fingerprints,noe-dy-neut-scatt,Chodera2014,ben-rev-msm,simon-mech-mod-nmr,oom-feliks,simon-amm},
we also recommend the literature on TICA~\cite{tica,tica3,kinetic-maps,mdtutorial},
transition path theory (TPT)~\cite{weinan-tpt,metzner-msm-tpt},
hidden Markov state models (HMMs)~\cite{noe-proj-hid-msm,jhp-spectral-rate-theory,bhmm-preprint},
and variational techniques~\cite{noe-vac,vamp-preprint,gmrq},
as these topics play important roles within the standard MSM workflow.

>>>>

In addition to publications on the theory and application of Markov state modeling~\cite{schuette-msm,buchete-msm-2008,noe-tmat-sampling,bowman-msm-2009,noe-folding-pathways,sarich-msm-quality,noe-fingerprints,noe-dy-neut-scatt,Chodera2014,ben-rev-msm,simon-mech-mod-nmr,oom-feliks,simon-amm},
we also recommend the literature on TICA~\cite{tica,tica3,kinetic-maps,tica2},
transition path theory (TPT)~\cite{weinan-tpt,metzner-msm-tpt},
hidden Markov state models (HMMs)~\cite{noe-proj-hid-msm,jhp-spectral-rate-theory,bhmm-preprint},
and variational techniques~\cite{noe-vac,vamp-preprint,gmrq},
as these topics play important roles within the standard MSM workflow.
